Enforced Invariant Confluence

### 2016-11-23 doc/counters.tex
Added and shrunk figures.

\begin{figure}
  \newenvironment{griddedpic}{
    \begin{tikzpicture}
      \clip (-4, -1) rectangle (4, 4);
  }{
      \draw (-4, -1) grid (4, 4);
      \draw[ultra thick] (-4, 0) -- (4, 0);
      \draw[ultra thick] (0, -1) -- (0, 4);
    \end{tikzpicture}
  }

  \begin{subfigure}[c]{0.5\textwidth}
    \begin{griddedpic}
      \fill[red, opacity=0.4]
        (-10, 10) -- (10, -10) -- (10, 10) -- cycle;
    \end{griddedpic}
    \caption{$\inva$}
  \end{subfigure}
  \begin{subfigure}[c]{0.5\textwidth}
    \begin{griddedpic}
      \fill[blue, opacity=0.4]
        (-10, -10) -- (10, 10) -- (-10, 10) -- cycle;
    \end{griddedpic}
    \caption{$\invb$}
  \end{subfigure}

  \vspace{0.5cm}

  \begin{subfigure}[c]{0.5\textwidth}
    \begin{griddedpic}
      \fill[green, opacity=0.4]
        (-10, 1) -- (10, 1) -- (10, 10) -- (-10, 10) -- cycle;
    \end{griddedpic}
    \caption{$\invc$}
  \end{subfigure}
  \begin{subfigure}[c]{0.5\textwidth}
    \begin{griddedpic}
      \fill[orange, opacity=0.4]
        (-10, 3) -- (10, 3) -- (10, 10) -- (-10, 10) -- cycle;
    \end{griddedpic}
  \caption{$\invd$}
  \end{subfigure}

  \vspace{0.5cm}

  \begin{subfigure}[c]{\textwidth}
    \centering
    \begin{griddedpic}
      \fill[purple, opacity=0.4]
        (-1, 1) -- (-3, 3) -- (-10, 3) -- (-10, 10) -- (10, 10) -- (10, 3) --
        (3, 3) -- (1, 1) -- cycle;
    \end{griddedpic}
    \caption{$\inv$}
  \end{subfigure}

@@

\begin{theorem}\label{thm:one-is-enough}
  For all sets of transactions $T$ and invariants $I$, T is 1-\iconfluent{} if
  and only if it is \iconfluent{}.
\end{theorem}
\begin{proof}
  The reverse direction is immediate from the definition of \iconfluence{}. For
  the forward direction, consider a set of transactions $T$ that is
  1-\iconfluent{} with respect to an invariant $I$, but assume for
  contradiction that $T$ is not \iconfluent{} with respect to $I$. That is,
  there exists a database state $D$ and two chains $C^1 = t^1_1, t^1_2, \ldots,
  t^1_m$ and $C^2 = t^2_1, t^2_2, \ldots, t^2_n$ such that $D$ satisfies $I$,
  $C^1$ satisfies $I$ starting at $D$, and $C^2$ satisfies $I$ starting at $D$,
  but $D \circ C^1 \circ C^2$ does not satisfy $I$.

  Let $C^z_j$ denote the prefix of $C^z$ of length $j$. We show by strong
  mathematical induction on $i$, that $D \circ C^1_j \circ C^2_k$ satisfies $I$
  for all $0 \leq j \leq m$, $0 \leq k \leq n$, and $0 \leq i = j + k \leq n +
  m$.
  %
  The base case, when $i = 0$, is trivial. $j = k = 0$, and $D \circ C^1_0
  \circ C^2_0 = D$ which satisfies $I$ by assumption.
  %
  For the inductive step, we wish to show for arbitrary $0 \leq j \leq m$, $0
  \leq k \leq n$, and $i = j + k$ that $D \circ C^1_j \circ C^2_k$ satisfies
  $I$. If $j = 0$, then $D \circ C^1_0 \circ C^2_k = D \circ C^2_k$ satisfies
  $I$ by the assumption that $C^2$ satisfies $I$ starting at $D$, and likewise
  for when $k = 0$. Now consider $j, k > 0$. By the inductive hypothesis, we
  know
    (1) $D \circ C^1_{j-1} \circ C^2_{k-1}$,
    (2) $D \circ C^1_{j-1} \circ C^2_{k}$, and
    (3) $D \circ C^1_{j}   \circ C^2_{k-1}$
  all satisfy $I$. If we let (1) be our initial database state, $t^1_j$ be one
  chain, and $t^2_k$ be the other chain, then the 1-\iconfluence{} of $T$ tells
  us that $(1) \circ t^1_j \circ t^2_k = D \circ C^1_j \circ C^2_k$ satisfies
  $I$.
\end{proof}

@@

  \begin{subfigure}[b]{0.32\textwidth}
    \centering
    \begin{tikzpicture}
      \gridxy{}
      \forxy{\node[point] (\x-\y) at (\x, \y) {};}
    \end{tikzpicture}
    \caption{Visualization of $I$.}
    \label{fig:wimp-iviz}
  \end{subfigure}

  \begin{subfigure}[b]{0.32\textwidth}
    \centering
    \begin{tikzpicture}
      \gridxy{}
      \forxy{\node[point] (\x-\y) at (\x, \y) {};}
      \forxy{\draw[vec] (\x, \y) -- (\x, \y + 1);}
    \end{tikzpicture}
    \caption{Visualization of $c_1$.}
    \label{fig:wimp-c1viz}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \centering
    \begin{tikzpicture}
      \gridxy{}
      \forxy{\node[point] (\x-\y) at (\x, \y) {};}
      \forxysmall{\draw[vec] (\x, \y) -- (\x + \x + 1, \y);}
    \end{tikzpicture}
    \caption{Visualization of $c_2$.}
    \label{fig:wimp-c2viz}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \centering
    \begin{tikzpicture}
      \gridxy{}
      \forxy{\node[point] (\x-\y) at (\x, \y) {};}
      \forxysmall{\draw[vec] (\x, \y) -- (\x + \x - 1, \y);}
    \end{tikzpicture}
    \caption{Visualization of $c_3$.}
    \label{fig:wimp-c3viz}
  \end{subfigure}

@@

\begin{itemize}
  \item \todo{Clarify these rambling thoughts.}
  \item \todo{Add $k$-\isafety to the figure.}
  \item \todo{Find something between \isafety{} and \iconfluence.}
\end{itemize}

\begin{itemize}
  \item \textbf{1-\isafety.}
    $\forall D, D', c.\>
      I(D) \land
      I(D') \implies
      I(D \circ \denote{c}(D'))$

  \item \textbf{k-\isafety.}
    $\forall D, D', B, C, c.\>
        C = \denote{B}(D) \land
       |B| \leq k-1 \land
       I(C @ D) \land
       I(B @ D') \implies
       I(D \circ C \circ \denote{c}(D' \circ C))$

  \item \textbf{\isafety.}
    $\forall D, D', B, C, c.\>
        C = \denote{B}(D) \land
       I(C @ D) \land
       I(B @ D') \implies
       I(D \circ C \circ \denote{c}(D' \circ C))$

@@

\tikzstyle{txn}=[ultra thick, ->]
\tikzstyle{dtxn}=[ultra thick, ->, dashed]
\tikzstyle{impl}=[-implies, double distance=3pt]
\newcommand{\inode}[3][]{
  \node[draw, shape=circle, minimum width=0.5cm, #1] (#2) at (#3) {};
  \node[fill, shape=circle] () at (#3) {};
}
\newcommand{\nnode}[3][]{
  \node[fill, shape=circle, #1] (#2) at (#3) {};
}

@@

  \begin{tikzpicture}
    \node[] (isafety) at (0, 0) {\isafety};
    \node[] (ipreservation) at ($(isafety) + (30:3)$) {\ipreservation};
    \node[] (iconfluence) at ($(isafety) + (-30:3)$) {\iconfluence};
    \node[] (k-iconfluence) at ($(iconfluence) + (4, 0)$) {$k$-\iconfluence};
    \node[] (1-iconfluence) at ($(k-iconfluence) + (4, 0)$) {1-\iconfluence};

    \draw[impl] (isafety) -> (ipreservation);
    \draw[impl] (isafety) -> (iconfluence);
    \draw[impl] (iconfluence) -> (k-iconfluence);
    \draw[impl] (k-iconfluence) -> (1-iconfluence);
  \end{tikzpicture}

@@

    \begin{tikzpicture}[scale=2]
      \inode[label=above:$D_0$]{l1}{0, 4}
      \inode[label=left:$D_1$]{l2}{0, 3}
      \inode[label=left:$D_{n-1}$]{l3}{0, 1}
      \nnode{l4}{0, 0}

@@

      \draw[dtxn] (l1) -- (l2) node[midway, left]{$\denote{c_1}(D_0')$};
      \draw[dtxn] (l2) -- (l3) node[midway, left]{
        $\begin{array}{l}
          \denote{c_2}(D_1'), \\
          \ldots, \\
          \denote{c_{n-1}}(D_{n-2}'), \\
        \end{array}$
      };
      \draw[dtxn] (l3) -- (l4) node[midway, left]{$\denote{c_n}(D_{n-1}')$};
    \end{tikzpicture}

@@

    \begin{tikzpicture}[scale=2]
      \inode[label=above:{$D = D_{t_0} = D_{u_0}$}]{a}{0, 0}
      \inode[label=left:$D_{t_1}$]{l1}{$(a) + (240:1.5)$}
      \inode[label=left:$D_{t_n}$]{l2}{$(l1) + (0, -2)$}
      \inode[label=right:$D_{u_1}$]{r1}{$(a) + (300:1.5)$}
      \inode[label=right:$D_{u_m}$]{r2}{$(r1) + (0, -2)$}
      \nnode{b}{$(l2) + (300:1.5)$}

>>>>

\begin{figure}
  \newenvironment{griddedpic}{
    \begin{tikzpicture}[scale=0.4]
      \clip (-4, -1) rectangle (4, 4);
  }{
      \draw (-4, -1) grid (4, 4);
      \draw[ultra thick] (-4, 0) -- (4, 0);
      \draw[ultra thick] (0, -1) -- (0, 4);
    \end{tikzpicture}
  }

  \begin{subfigure}[b]{0.24\textwidth}
    \centering
    \begin{griddedpic}
      \fill[red, opacity=0.4]
        (-10, 10) -- (10, -10) -- (10, 10) -- cycle;
    \end{griddedpic}
    \caption{$\inva$}
  \end{subfigure}
  \begin{subfigure}[b]{0.24\textwidth}
    \centering
    \begin{griddedpic}
      \fill[blue, opacity=0.4]
        (-10, -10) -- (10, 10) -- (-10, 10) -- cycle;
    \end{griddedpic}
    \caption{$\invb$}
  \end{subfigure}
  \begin{subfigure}[b]{0.24\textwidth}
    \centering
    \begin{griddedpic}
      \fill[green, opacity=0.4]
        (-10, 1) -- (10, 1) -- (10, 10) -- (-10, 10) -- cycle;
    \end{griddedpic}
    \caption{$\invc$}
  \end{subfigure}
  \begin{subfigure}[b]{0.24\textwidth}
    \centering
    \begin{griddedpic}
      \fill[orange, opacity=0.4]
        (-10, 3) -- (10, 3) -- (10, 10) -- (-10, 10) -- cycle;
    \end{griddedpic}
  \caption{$\invd$}

  \end{subfigure}
  \begin{subfigure}[b]{\textwidth}
    \centering
    \begin{griddedpic}
      \fill[purple, opacity=0.4]
        (-1, 1) -- (-3, 3) -- (-10, 3) -- (-10, 10) -- (10, 10) -- (10, 3) --
        (3, 3) -- (1, 1) -- cycle;
    \end{griddedpic}
    \caption{$\inv$}
  \end{subfigure}

@@

\begin{theorem}\label{thm:one-is-enough}
  For all sets of transactions $T$ and invariants $I$, T is 1-\iconfluent{} if
  and only if it is \iconfluent{}.
\end{theorem}
\begin{proof}
  The reverse direction is immediate from the definition of \iconfluence{}. For
  the forward direction, consider a set of transactions $T$ that is
  1-\iconfluent{} with respect to an invariant $I$, but assume for
  contradiction that $T$ is not \iconfluent{} with respect to $I$. That is,
  there exists a database state $D$ and two chains $C^t = t_1, t_2, \ldots,
  t_m$ and $C^u = u_1, u_2, \ldots, u_n$ such that $D$ satisfies $I$,
  $C^t$ satisfies $I$ starting at $D$, and $C^u$ satisfies $I$ starting at $D$,
  but $D \circ C^t \circ C^u$ does not satisfy $I$.

  Let $C^z_j$ denote the prefix of $C^z$ of length $j$. We show by strong
  mathematical induction on $i$, that $D \circ C^t_j \circ C^u_k$ satisfies $I$
  for all $0 \leq j \leq m$, $0 \leq k \leq n$, and $0 \leq i = j + k \leq n +
  m$.
  %
  The base case, when $i = 0$, is trivial. $j = k = 0$, and $D \circ C^t_0
  \circ C^u_0 = D$ which satisfies $I$ by assumption.
  %
  For the inductive step, we wish to show for arbitrary $0 \leq j \leq m$, $0
  \leq k \leq n$, and $i = j + k$ that $D \circ C^t_j \circ C^u_k$ satisfies
  $I$. If $j = 0$, then $D \circ C^t_0 \circ C^u_k = D \circ C^u_k$ satisfies
  $I$ by the assumption that $C^u$ satisfies $I$ starting at $D$, and likewise
  for when $k = 0$. Now consider $j, k > 0$. By the inductive hypothesis, we
  know
    (1) $D \circ C^t_{j-1} \circ C^u_{k-1}$,
    (2) $D \circ C^t_{j-1} \circ C^u_{k}$, and
    (3) $D \circ C^t_{j}   \circ C^u_{k-1}$
  all satisfy $I$. If we let (1) be our initial database state, $t_j$ be one
  chain, and $u_k$ be the other chain, then the 1-\iconfluence{} of $T$ tells
  us that $(1) \circ t_j \circ u_k = D \circ C^t_j \circ C^u_k$ satisfies
  $I$.
\end{proof}

\newcommand{\baseedges}{
  \begin{scope}[on background layer]
    \draw[txn] (03) -- (13) node[midway, above]{$u_1$};
    \draw[txn] (13) -- (23) node[midway, above]{$u_2$};
    \draw[txn] (23) -- (33) node[midway, above]{$u_3$};
    \draw[txn] (03) -- (02) node[midway, left]{$t_1$};
    \draw[txn] (02) -- (01) node[midway, left]{$t_2$};
    \draw[txn] (01) -- (00) node[midway, left]{$t_3$};
    \draw[dtxn] (00) -- (30);
    \draw[dtxn] (33) -- (30);
  \end{scope}
}

\begin{figure}[h]
  \centering
  \newcommand{\onescale}{1.1}

  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \begin{tikzpicture}[scale=\onescale]
      \foreach \x/\y in {
        0/3, 1/3, 2/3, 3/3,
        0/2,
        0/1,
        0/0%
      } {
        \inode{\x\y}{\x, \y}
      }
      \nnode{30}{3, 0}
      \baseedges{}
    \end{tikzpicture}
    \caption{}
    \label{}
  \end{subfigure}
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \begin{tikzpicture}[scale=\onescale]
      \foreach \x/\y in {
             1/3, 2/3, 3/3,
        0/2,
        0/1,
        0/0%
      } {
        \inode{\x\y}{\x, \y}
      }
      \foreach \x/\y in {0/3} {
        \inode[red]{\x\y}{\x, \y}
      }
      \nnode{30}{3, 0}
      \baseedges{}
    \end{tikzpicture}
    \caption{}
    \label{}
  \end{subfigure}
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \begin{tikzpicture}[scale=\onescale]
      \foreach \x/\y in {
        0/3,      2/3, 3/3,
        %
        0/1,
        0/0%
      } {
        \inode{\x\y}{\x, \y}
      }
      \foreach \x/\y in {0/2, 1/3} {
        \inode[red]{\x\y}{\x, \y}
      }
      \nnode{30}{3, 0}
      \baseedges{}
    \end{tikzpicture}
    \caption{}
    \label{}
  \end{subfigure}

  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \begin{tikzpicture}[scale=\onescale]
      \foreach \x/\y in {
        0/3, 1/3,      3/3,
        0/2,
        %
        0/0%
      } {
        \inode{\x\y}{\x, \y}
      }
      \foreach \x/\y in {0/1, 1/2, 2/3} {
        \inode[red]{\x\y}{\x, \y}
      }
      \nnode{30}{3, 0}
      \baseedges{}
      \draw[txn] (02) -- (12) node[midway, above] {$u_1$};
      \draw[txn] (13) -- (12) node[midway, left]  {$t_1$};
    \end{tikzpicture}
    \caption{}
    \label{}
  \end{subfigure}
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \begin{tikzpicture}[scale=\onescale]
      \foreach \x/\y in {
        0/3, 1/3, 2/3,
        0/2, 1/2,
        0/1%
        %
      } {
        \inode{\x\y}{\x, \y}
      }
      \foreach \x/\y in {0/0, 1/1, 2/2, 3/3} {
        \inode[red]{\x\y}{\x, \y}
      }
      \nnode{30}{3, 0}
      \baseedges{}
      \draw[txn] (02) -- (12) node[midway, above] {$u_1$};
      \draw[txn] (13) -- (12) node[midway, left]  {$t_1$};
      \draw[txn] (01) -- (11) node[midway, above] {$u_1$};
      \draw[txn] (12) -- (11) node[midway, left]  {$t_2$};
      \draw[txn] (12) -- (22) node[midway, above] {$u_2$};
      \draw[txn] (23) -- (22) node[midway, left]  {$t_1$};
    \end{tikzpicture}
    \caption{}
    \label{}
  \end{subfigure}
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \begin{tikzpicture}[scale=\onescale]
      \foreach \x/\y in {
        0/3, 1/3, 2/3, 3/3,
        0/2, 1/2, 2/2,
        0/1, 1/1,
        0/0%
      } {
        \inode{\x\y}{\x, \y}
      }
      \foreach \x/\y in {1/0, 2/1, 3/2} {
        \inode[red]{\x\y}{\x, \y}
      }
      \nnode{30}{3, 0}
      \baseedges{}
      \draw[txn] (02) -- (12) node[midway, above] {$u_1$};
      \draw[txn] (13) -- (12) node[midway, left]  {$t_1$};
      \draw[txn] (01) -- (11) node[midway, above] {$u_1$};
      \draw[txn] (12) -- (11) node[midway, left]  {$t_2$};
      \draw[txn] (12) -- (22) node[midway, above] {$u_2$};
      \draw[txn] (23) -- (22) node[midway, left]  {$t_1$};
      \draw[txn] (00) -- (10) node[midway, above] {$u_1$};
      \draw[txn] (11) -- (10) node[midway, left]  {$t_3$};
      \draw[txn] (11) -- (21) node[midway, above] {$u_2$};
      \draw[txn] (22) -- (21) node[midway, left]  {$t_2$};
      \draw[txn] (22) -- (32) node[midway, above] {$u_3$};
      \draw[txn] (33) -- (32) node[midway, left]  {$t_1$};
    \end{tikzpicture}
    \caption{}
    \label{}
  \end{subfigure}

  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \begin{tikzpicture}[scale=\onescale]
      \foreach \x/\y in {
        0/3, 1/3, 2/3, 3/3,
        0/2, 1/2, 2/2, 3/2,
        0/1, 1/1, 2/1,
        0/0, 1/0%
      } {
        \inode{\x\y}{\x, \y}
      }
      \foreach \x/\y in {2/0, 3/1} {
        \inode[red]{\x\y}{\x, \y}
      }
      \nnode{30}{3, 0}
      \baseedges{}
      \draw[txn] (02) -- (12) node[midway, above] {$u_1$};
      \draw[txn] (13) -- (12) node[midway, left]  {$t_1$};
      \draw[txn] (01) -- (11) node[midway, above] {$u_1$};
      \draw[txn] (12) -- (11) node[midway, left]  {$t_2$};
      \draw[txn] (12) -- (22) node[midway, above] {$u_2$};
      \draw[txn] (23) -- (22) node[midway, left]  {$t_1$};
      \draw[txn] (00) -- (10) node[midway, above] {$u_1$};
      \draw[txn] (11) -- (10) node[midway, left]  {$t_3$};
      \draw[txn] (11) -- (21) node[midway, above] {$u_2$};
      \draw[txn] (22) -- (21) node[midway, left]  {$t_2$};
      \draw[txn] (22) -- (32) node[midway, above] {$u_3$};
      \draw[txn] (33) -- (32) node[midway, left]  {$t_1$};
      \draw[txn] (10) -- (20) node[midway, above] {$u_2$};
      \draw[txn] (21) -- (20) node[midway, left]  {$t_3$};
      \draw[txn] (21) -- (31) node[midway, above] {$u_3$};
      \draw[txn] (32) -- (31) node[midway, left]  {$t_2$};
    \end{tikzpicture}
    \caption{}
    \label{}
  \end{subfigure}
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \begin{tikzpicture}[scale=\onescale]
      \foreach \x/\y in {
        0/3, 1/3, 2/3, 3/3,
        0/2, 1/2, 2/2, 3/2,
        0/1, 1/1, 2/1, 3/1,
        0/0, 1/0, 2/0%
      } {
        \inode{\x\y}{\x, \y}
      }
      \inode[red]{30}{3, 0}
      \baseedges{}
      \draw[txn] (02) -- (12) node[midway, above] {$u_1$};
      \draw[txn] (13) -- (12) node[midway, left]  {$t_1$};
      \draw[txn] (01) -- (11) node[midway, above] {$u_1$};
      \draw[txn] (12) -- (11) node[midway, left]  {$t_2$};
      \draw[txn] (12) -- (22) node[midway, above] {$u_2$};
      \draw[txn] (23) -- (22) node[midway, left]  {$t_1$};
      \draw[txn] (00) -- (10) node[midway, above] {$u_1$};
      \draw[txn] (11) -- (10) node[midway, left]  {$t_3$};
      \draw[txn] (11) -- (21) node[midway, above] {$u_2$};
      \draw[txn] (22) -- (21) node[midway, left]  {$t_2$};
      \draw[txn] (22) -- (32) node[midway, above] {$u_3$};
      \draw[txn] (33) -- (32) node[midway, left]  {$t_1$};
      \draw[txn] (10) -- (20) node[midway, above] {$u_2$};
      \draw[txn] (21) -- (20) node[midway, left]  {$t_3$};
      \draw[txn] (21) -- (31) node[midway, above] {$u_3$};
      \draw[txn] (32) -- (31) node[midway, left]  {$t_2$};
      \draw[txn] (20) -- (30) node[midway, above] {$u_3$};
      \draw[txn] (31) -- (30) node[midway, left]  {$t_3$};
    \end{tikzpicture}
    \caption{}
    \label{}
  \end{subfigure}

  \caption{TODO}
  \label{fig:one-is-enough}
\end{figure}

@@

  \begin{subfigure}[b]{0.49\textwidth}
    \centering
    \begin{tikzpicture}[scale=0.8]
      \gridxy{}
      \forxy{\node[point] (\x-\y) at (\x, \y) {};}
    \end{tikzpicture}
    \caption{Visualization of $I$.}
    \label{fig:wimp-iviz}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \centering
    \begin{tikzpicture}[scale=0.8]
      \gridxy{}
      \forxy{\node[point] (\x-\y) at (\x, \y) {};}
      \forxy{\draw[vec] (\x, \y) -- (\x, \y + 1);}
    \end{tikzpicture}
    \caption{Visualization of $c_1$.}
    \label{fig:wimp-c1viz}
  \end{subfigure}

  \begin{subfigure}[b]{0.49\textwidth}
    \centering
    \begin{tikzpicture}[scale=0.8]
      \gridxy{}
      \forxy{\node[point] (\x-\y) at (\x, \y) {};}
      \forxysmall{\draw[vec] (\x, \y) -- (\x + \x + 1, \y);}
    \end{tikzpicture}
    \caption{Visualization of $c_2$.}
    \label{fig:wimp-c2viz}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \centering
    \begin{tikzpicture}[scale=0.8]
      \gridxy{}
      \forxy{\node[point] (\x-\y) at (\x, \y) {};}
      \forxysmall{\draw[vec] (\x, \y) -- (\x + \x - 1, \y);}
    \end{tikzpicture}
    \caption{Visualization of $c_3$.}
    \label{fig:wimp-c3viz}
  \end{subfigure}

@@

\begin{itemize}
  \item \todo{Clarify these rambling thoughts.}
  \item \todo{Add $k$-\isafety to the figure.}
  \item \todo{Find something between \isafety{} and \iconfluence.}
  \item \todo{Add two state-based proof rules from strong enough paper limited
              to causal consistency.}
  \item \todo{Prove state-based proof rules imply iconfluence.}
  \item \todo{Figure out relationship of proof rules to this stuff.}
  \item \todo{1-iconfluence with derived txns to start}
\end{itemize}

\begin{itemize}
  \item \textbf{0-\isafety.}
    $\forall D, D', c.\>
      I(D) \land
      I(D') \implies
      I(D \circ \denote{c}(D'))$

  \item \textbf{k-\isafety.}
    $\forall D, D', B, C, c.\>
       C = \denote{B}(D) \land
       |B| \geq k \land
       I(B @ D') \implies
       I(D \circ C \circ \denote{c}(D' \circ C))$

  \item \textbf{\isafety.}
    $\forall D, D', B, C, c.\>
       C = \denote{B}(D) \land
       I(B @ D') \implies
       I(D \circ C \circ \denote{c}(D' \circ C))$

@@

@@

  \begin{tikzpicture}
    \node[] (0-isafety) at (0, 0) {0-\isafety};
    \node[] (ipreservation) at ($(0-isafety) + (30:3)$) {\ipreservation};
    \node[] (iconfluence) at ($(0-isafety) + (-30:3)$) {\iconfluence};
    \node[] (k-iconfluence) at ($(iconfluence) + (4, 0)$) {$k$-\iconfluence};
    \node[] (1-iconfluence) at ($(k-iconfluence) + (4, 0)$) {1-\iconfluence};

    \draw[impl] (0-isafety) -> (ipreservation);
    \draw[impl] (0-isafety) -> (iconfluence);
    \draw[impl] (iconfluence) -> (k-iconfluence);
    \draw[impl] (k-iconfluence) -> (1-iconfluence);
  \end{tikzpicture}

@@

    \begin{tikzpicture}[scale=2]
      \inode[label=above:$D_0$]{l1}{0, 4}
      \nnode{l4}{0, 0}

@@

      \draw[dtxn] (l1) -- (l4) node[midway, left]{
        $\begin{array}{l}
          \denote{c_1}(D_0') \circ {} \\
          \denote{c_2}(D_1') \circ {} \\
          \cdots \circ {} \\
          \denote{c_n}(D_{n-1}')
        \end{array}$
      };
    \end{tikzpicture}

@@

    \begin{tikzpicture}[scale=2]
      \inode[label=above:{$D = D_{t_0} = D_{u_0}$}]{a}{0, 0}
      \inode[label=left:$D_{t_1}$]{l1}{$(a) + (240:1)$}
      \inode[label=left:$D_{t_n}$]{l2}{$(l1) + (240:2)$}
      \inode[label=right:$D_{u_1}$]{r1}{$(a) + (300:1)$}
      \inode[label=right:$D_{u_m}$]{r2}{$(r1) + (300:2)$}
      \nnode{b}{$(l2) + (300:3)$}
